---
title: "Implications Analysis"
output: 
  html_notebook:
    code_folding: hide
---

```{r include = FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r, echo = FALSE, message = FALSE}
# Loading necessary packages
library(knitr)
library(tidyverse)
library(googlesheets)
library(stringr)
library(forcats)
library(scales)

# Setting global options
options(digits = 4)
```

First, we need to read in our data from Google Sheets.

```{r, include = FALSE}
sheet <- gs_title("implications_analysis")
implications <- gs_read(ss = sheet, ws = "Sayfa2", col_names = TRUE) %>% 
  select(year:subject, -general_term) %>% 
  mutate(
    study = factor(study, levels = c("D", "E", "ED"), 
                   labels = c("Development", "Exploration", "DevExp")),
    purpose = factor(purpose, levels = c("Ast", "Ent", "Int", "Res"),
                     labels = c("Assistive", "Entertaining", "Intervention",
                                "Research")),
    intervention = str_split(intervention, ";"),
    age_range = fct_explicit_na(
      factor(age_range, 
             levels = c("Pre", "Chi", "Ado", "Adu", "Eld"), 
             labels = c("Preschooler", "Child", "Adolescent", "Adult", "Elderly"), 
             ordered = TRUE),
      na_level = "Not Specified"
    ),
    use_context = fct_explicit_na(
      factor(use_context,
             levels = c("Sch", "Hom", "Wor", "Out", "Cli", "Vir"),
             labels = c("School", "Home", "Work", "Outdoor", "Clinical",
                        "Virtual")),
      na_level = "Not Specified"
    ),
    physical_platform = str_split(physical_platform, ";"),
    interface = str_split(interface, ";"),
    user1 = str_split(user1, ";"),
    user2 = str_split(user2, ";"),
    subject = factor(subject, levels = c("AS", "mid", "AI"), 
                     labels = c("Autism Specific", "mid", "Autism Independent"))
  ) %>% 
  unnest(intervention, .drop = FALSE) %>% 
  unnest(physical_platform, .drop = FALSE) %>% 
  unnest(interface, .drop = FALSE) %>% 
  unnest(user1, .drop = FALSE) %>% 
  unnest(user2) 
# %>% 
  # mutate(intervention = fct_explicit_na(as.factor(intervention), 
                                   # na_level = "not specified"))
```


# What physical platforms are used in each study type?

```{r}
ggplot(implications) +
  geom_bar(aes(physical_platform)) +
  facet_wrap(~ study, nrow = 3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Have a look at the actual values.

```{r}
kable(
  implications %>% 
    group_by(study, physical_platform) %>% 
    count() %>% 
    arrange(study, -n)
)
```

```{r}
ggplot(implications) +
  geom_bar(aes(physical_platform, fill = study)) +
  # facet_wrap(~ study, nrow = 3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# What interfaces are used with each study type?

```{r}
ggplot(implications) +
  geom_bar(aes(interface)) +
  facet_wrap(~ study, nrow = 3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Here are the counts:

```{r}
kable(
  implications %>% 
    group_by(study, interface) %>% 
    count() %>% 
    arrange(study, -n)
)
```

```{r}
ggplot(implications) +
  geom_bar(aes(interface, fill = study)) +
  # facet_wrap(~ study, nrow = 3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# What intervention points are used with each age group - purpose combination?

```{r}
ggplot(implications) +
  geom_bar(aes(intervention, fill = age_range)) +
  # scale_fill_grey() +
  facet_wrap(~ purpose) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# What intervention points are used with each age group?

```{r}
ggplot(implications) +
  geom_bar(aes(factor(intervention, 
                      levels = names(sort(table(intervention), 
                                          decreasing = TRUE))))) +
  facet_wrap(~ age_range, nrow = 5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
ggplot(implications) +
  geom_bar(aes(factor(intervention, 
                      levels = names(sort(table(intervention), 
                                          decreasing = TRUE))), 
               fill = age_range)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Here are the actual counts:

```{r}
kable(
  implications %>% 
    group_by(age_range, intervention) %>% 
    count() %>% 
    arrange(age_range, -n)
)
```

When we exclude the observations where the purpose is research, we have the following:

```{r}
implications %>% 
  filter(purpose != "Research") %>% 
  ggplot() +
  geom_bar(aes(intervention, fill = age_range)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Or maybe:

```{r}
implications %>% 
  filter(purpose != "Research") %>% 
  ggplot() +
  geom_bar(aes(age_range, fill = intervention)) +
  # scale_fill_grey() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



# What interfaces are used with each platform?

```{r}
ggplot(implications) +
  geom_bar(aes(interface, fill = physical_platform)) +
  # scale_fill_grey() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))
```

```{r}
ggplot(implications) +
  geom_bar(aes(interface, fill = physical_platform), position = "fill") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))
```


```{r}
ggplot(implications) +
  geom_bar(aes(interface, fill = physical_platform), position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8))
```
