---
title: "Quantitative Analysis"
output: html_notebook
---

```{r include = FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r, echo = FALSE, message = FALSE}
# Loading necessary packages
library(tidyverse)
library(googlesheets)
library(stringr)
library(forcats)
library(knitr)
library(VennDiagram)
library(scales)

# Setting global options
options(digits = 4)
```

**Note:** In case you're not interested in the code written for the analysis, feel free to use the "Code" drop-down menu in the top-right corner and select "Hide All Code". Furthermore, the code used to produce the tables is not displayed by default (set by us).

Let's start by getting some first understanding of our data. We will look at each of our tables, one by one, and get some very basic statistics from them, mailnly what is being used/done most frequently in the papers included in the study.


# Data Collection

Let's start by having a look at who is usually the data collector.

```{r}
data_collectors_temp <- data_collection %>% 
  mutate(
    data_collector = factor(data_collector, 
                            levels = names(sort(table(data_collector), 
                                                decreasing = TRUE)),
                            exclude = NULL),
    data_collector = fct_explicit_na(factor(data_collector), 
                                     na_level = "not specified"),
    # Creating a new var "collector_type" to plot
    collector_type = ifelse(
      data_collector %in% c("res1", "res2"),
      "researcher",
      ifelse(
        data_collector %in% c("therapist", "teacher", "parent", "other", 
                              "caregiver", "HCI_exp"), 
        "actor",
        "not specified"
      )
    ),
    collector_type = factor(collector_type, 
                            levels = c("researcher", "actor", "not specified"))
  ) %>% 
  # Keep only unique combinations of paper/study/technique/data_collector
  group_by(paper_id, study_id, technique_id, data_collector) %>% 
  distinct(.keep_all = TRUE) %>% 
  ungroup()

ggplot(data_collectors_temp) +
  geom_bar(aes(data_collector))

ggplot(data_collectors_temp) +
  geom_bar(aes(collector_type))
```

**Note:** "not specified" in the graph above is either "researcher" not explicitly specified or the data were collected by some system or the product itself.

Let's have a look at the actual values:

```{r, echo = FALSE, results = "asis"}
kable(
  data_collectors_temp %>% 
    group_by(data_collector) %>% 
    count(),
  caption = "Data Collectors",
  col.names = c("Data Collector", "Frequency")
)

```

```{r, echo = FALSE, results = "asis"}

kable(
  data_collectors_temp %>% 
    group_by(collector_type) %>% 
    count(),
  caption = "Types of Data Collectors",
  col.names = c("Data Collector Type", "Frequency")
)
```

Now, coming to the different ways of collecting the data, let's have a look at the number of times each collection menthod is used.

We will have a look at both the type of methods used and at which methoods are actually used, sorted from the most frequently used to the least frequently used. Let us try visualizing what is actually going on.

```{r}
data_collection_meth <- data_collection %>% 
  # Set qualitative/quantitative = 0, when mixed = 1
  mutate(
    qualitative = ifelse(mixed == 1, 0, qualitative),
    quantitative = ifelse(mixed == 1, 0, quantitative)
  ) %>% 
  # Create a "method" variable and a "status" that indicates whether a method is 
  # actually used for a specific paper/study/technique_id
  gather(method, status, -c(paper_id, study_id, technique_id, data_collector,
                            qualitative, quantitative, mixed)) %>%
  # Transform "method" to factor here to keep ALL levels
  mutate(
    method = factor(method, levels = names(table(method)))
  ) %>% 
  # Keep only those that are used and drop the "status"
  filter(status == 1) %>% 
  select(-status) %>% 
  # Create a "method_type" variable and a "status" that indicates whether it is 
  # actually used for a specific paper/study/technique_id
  gather(method_type, status, -c(paper_id, study_id, technique_id, 
                                 data_collector, method)) %>% 
  # Transform "method_type" to factor here to keep ALL levels
  mutate(method_type = factor(method_type)) %>% 
  # Keep only those that are used and drop the "status"
  filter(status == 1) %>% 
  select(paper_id, study_id, technique_id, data_collector, method_type, method,
         -status) %>% 
  # Keep unique paper/study/technique/method combos
  group_by(paper_id, study_id, technique_id, method) %>%
  distinct(.keep_all = TRUE) %>% 
  ungroup() %>% 
  # Transform "method" and "method_type" to factor again, in order to sort their 
  # levels according to the counts
  mutate(
    method_type = factor(method_type, levels = names(sort(table(method_type), 
                                                          decreasing = TRUE))),
    method = factor(method, levels = names(sort(table(method), 
                                                decreasing = TRUE)))
  ) %>% 
  arrange(paper_id, study_id, technique_id)

# Plot "method"
ggplot(data_collection_meth) + 
  geom_bar(mapping = aes(method)) + 
  scale_x_discrete(drop = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

Here is a table with the actual values:

```{r, echo = FALSE, results = "asis"}
kable(
  data_collection_meth %>%
  group_by(method) %>% 
  count(),
  caption = "Methods Usage Frequency",
  col.names = c("Method", "Frequency")
)
```

Now, let us have a look at the types of methods used the most.

```{r}
# PLot "method_type"

# ggplot(data_collection_meth) +
#   geom_bar(aes(method_type))

# The above is wrong: we're counting methods
# Try the following:
data_collection_meth_types <- data_collection_meth %>% 
  group_by(paper_id, study_id, technique_id) %>% 
  distinct(.keep_all = TRUE) %>%
  select(-c(data_collector, method))

ggplot(data_collection_meth_types) +
  geom_bar(aes(method_type))
```

As we did above, hereis a table with the actual values:

```{r, echo = FALSE, results = "asis"}
kable(
  data_collection_meth_types %>% 
    group_by(method_type) %>% 
    count(),
  caption = "Method Types Usage Frequency",
  col.names = c("Method Type", "Frequency")
)
```




# Design

Let's now have a look at the kind of product and/or service most oftened designed.

```{r}
design_type <- design %>% 
  gather(product, status, -paper_id) %>% 
  mutate(product = factor(product, levels = names(table(product)))) %>% 
  filter(status == 1) %>% 
  select(-status) %>% 
  mutate(
    product = factor(product, levels = names(sort(table(product), 
                                                  decreasing = TRUE)))
  ) %>% 
  arrange(paper_id)

ggplot(design_type) +
  geom_bar(aes(product)) +
  scale_x_discrete(drop = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Here are the actual values:

```{r, echo = FALSE, results = "asis"}
kable(
  design_type %>% 
    group_by(product) %>% 
    count(), 
  caption = "Product Type Usage Frequency",
  col.names = c("Product", "Frequency")
)
```


# Intervention

The interventions we observed are as follows:

```{r}
intervention_temp <- intervention %>% 
  select(-method) %>% 
  gather(intervention_type, status, -paper_id) %>% 
  # Transform intervention_type to factor here to keep ALL levels
  mutate(
    intervention_type = factor(intervention_type, 
                               levels = names(table(intervention_type)))
  ) %>% 
  # Keep only the intervantions that actually appear in the papers
  filter(status == 1) %>% 
  select(-status) %>% 
  # Transform intervention_type to factor here again, so its levels are in 
  # decreasing order
  mutate(
    intervention_type = factor(
      intervention_type, 
      levels = names(sort(table(intervention_type), decreasing = TRUE))
    )
  ) %>% 
  arrange(paper_id)


```

```{r}
ggplot(intervention_temp) +
  geom_bar(aes(intervention_type)) +
  scale_x_discrete(drop = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
ggplot(intervention_temp) +
  geom_bar(aes(intervention_type, ..prop.., group = 1)) +
  scale_x_discrete(drop = FALSE) +
  scale_y_continuous(labels = percent) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


**Note:** We will need to check what the picture is when we group the different kinds of interventions together.

Here are the individual values:

```{r, echo = FALSE, results = "asis"}
kable(
  intervention_temp %>% 
    group_by(intervention_type) %>% 
    summarize(n = n()) %>% 
    mutate(percentage = percent(n / sum(n)))
)
```



# Participants

We need to create an age variable.

```{r}
participants_age <- participants %>%
  mutate(
    age1 = ifelse(
      age_min <= 4 & age_max <= 4,
      "1",
      ifelse(
        age_min <= 4 & (age_max >= 5 & age_max <= 12),
        "1;2",
        ifelse(
          age_min <= 4 & (age_max >= 13 & age_max <= 19),
          "1;2;3",
          ifelse(
            age_min <= 4 & age_max >= 20,
            "1;2;3;4",
            ifelse(
              (age_min >= 5 & age_min <= 12) & (age_max >= 5 & age_max <= 12),
              "2",
              ifelse(
                (age_min >= 5 & age_min <= 12) &
                  (age_max >= 13 & age_max <= 19),
                "2;3",
                ifelse(
                  (age_min >= 5 & age_min <= 12) & age_max >= 20,
                  "2;3;4",
                  ifelse(
                    (age_min >= 13 & age_min <= 19) &
                      (age_max >= 13 & age_max <= 19),
                    "3",
                    ifelse(
                      (age_min >= 13 & age_min <= 19) & age_max >= 20,
                      "3;4",
                      ifelse(
                        age_min >= 20 & age_max >= 20,
                        "4",
                        ifelse(
                          age_min > age_max,
                          "AGE_RANGE_ERROR",
                          ifelse(
                            is.na(age_min) & is.na(age_max) &
                              is.na(age_mean) & is.na(dev_stage),
                            "missing",
                            NA
                          )
                        )
                      )
                    )
                  )
                )
              )
            )
          )
        )
      )
    ),
    age2 = ifelse(
      is.na(age_min) & is.na(age_max) & age_mean < 5,
      "1",
      ifelse(
        is.na(age_min) & is.na(age_max) &
          age_mean > 5 & age_mean < 13,
        "2",
        ifelse(
          is.na(age_min) & is.na(age_max) &
            age_mean > 13 & age_mean < 20,
          "3",
          ifelse(
            is.na(age_min) & is.na(age_max) &
              age_mean > 20,
            "4",
            ifelse(
              is.na(age_min) & is.na(age_max) &
                is.na(age_mean) & is.na(dev_stage),
              "missing",
              NA
            )
          )
        )
      )
    ),
    age3 = ifelse(
      is.na(age_min) & is.na(age_max) &
        is.na(age_mean) &
        dev_stage %in% c("infant", "toddler",
                         "preschooler"),
      "1",
      ifelse(
        is.na(age_min) & is.na(age_max) &
          is.na(age_mean) &
          dev_stage == "child",
        "2",
        ifelse(
          is.na(age_min) & is.na(age_max) &
            is.na(age_mean) &
            dev_stage == "adolescent",
          "3",
          ifelse(
            is.na(age_min) & is.na(age_max) &
              is.na(age_mean) &
              dev_stage %in% c("young adult",
                               "adult",
                               "middle age",
                               "old age"),
            "4",
            ifelse(
              is.na(age_min) & is.na(age_max) &
                is.na(age_mean) & is.na(dev_stage),
              "missing",
              NA
            )
          )
        )
      )
    ),
    age_to_split = ifelse(
      is.na(age1) & is.na(age2) & is.na(age3),
      NA,
      ifelse(
        !is.na(age1),
        age1,
        ifelse(
          !is.na(age2),
          age2,
          ifelse(
            !is.na(age3),
            age3,
            "ERROR"
          )
        )
      )
    )
  ) %>%
  mutate(age = str_split(age_to_split, ";")) %>%
  unnest(age) %>%
  mutate(age = fct_explicit_na(factor(age, levels = 1:4,
                                      labels = c("preschooler", "child",
                                                 "adolescent", "adult")),
                               na_level = "not specified")) %>% 
  select(-c(age1, age2, age3, age_to_split, age_min, age_max, age_mean,
            dev_stage))
```


## Which age category is used the most?

```{r}
ggplot(participants_age) +
  geom_bar(aes(age))
```

As percentages:

```{r}
ggplot(participants_age) +
  geom_bar(aes(age, ..prop.., group = 1)) +
  scale_y_continuous(labels = percent)
```


And the values:

```{r}
kable(
  participants_age %>% 
  select(age) %>% 
  group_by(age) %>% 
  summarize(n = n()) %>% 
  mutate(percentage = percent(n / sum(n)))
)
```

## In which age categories are the ASD participants?

**Moved to the end**



```{r}
participants_temp <- participants %>% 
  gather(diagnosis, num_diagnosis, c(ASD:other)) %>% 
  mutate(
    diagnosis = factor(diagnosis, levels = names(table(diagnosis))),
    diagnosis_type = ifelse(
      diagnosis %in% c("ASD", "HFA", "MFA", "LFA", "PDD", "severe"),
      "ASD",
      ifelse(
        diagnosis %in% c("ID", "dyslexia", "ADHD", "other"), 
        "non-ASD", 
        ifelse(
          diagnosis == "TD",
          "typically developed",
          "unknown"
        )
      )
    ),
    diagnosis_type = factor(diagnosis_type, 
                            levels = names(table(diagnosis_type)))
  ) %>% 
  filter(num_diagnosis > 0 | is.na(num_diagnosis)) %>% 
  mutate(
    diagnosis = factor(
      diagnosis,
      levels = names(sort(table(diagnosis), decreasing = TRUE))
    )
  ) %>% 
  arrange(paper_id, group_id)

participants_mixed_index <- participants_temp %>%
  group_by(paper_id, group_id) %>%
  summarize(n_types = n_distinct(diagnosis_type)) %>%
  filter(n_types > 1) %>%
  select(paper_id, group_id) %>% 
  mutate(diagnosis_mixed = 1)

participants_temp <- participants_temp %>% 
  left_join(participants_mixed_index, by = c("paper_id", "group_id")) %>% 
  mutate(
    diagnosis_type = ifelse(diagnosis_mixed == 1, "mixed", diagnosis_type),
    diagnosis_type = ifelse(
      diagnosis %in% c("ASD", "HFA", "MFA", "LFA", "PDD", "severe") & 
        is.na(diagnosis_mixed), 
      "ASD", 
      ifelse(
        diagnosis %in% c("ID", "dyslexia", "ADHD", "other") & 
          is.na(diagnosis_mixed), 
        "non-ASD", 
        ifelse(
          diagnosis == "TD" & is.na(diagnosis_mixed),
          "typically developed",
          diagnosis_type
        )
      )
    ), 
    diagnosis_type = factor(
      diagnosis_type, 
      levels = names(sort(table(diagnosis_type), 
                          decreasing = TRUE))
    )
  )

participants_diagnosis <- participants_temp %>% 
  select(paper_id, group_id, diagnosis_type, diagnosis, num_diagnosis)

participants_diagnosis_type <- participants_temp %>% 
  group_by(paper_id, group_id) %>% 
  select(paper_id, group_id, diagnosis, diagnosis_type, diagnosis_mixed) %>% 
  distinct(.keep_all = TRUE) %>% 
  select(-diagnosis, -diagnosis_mixed)

participants_info <- participants %>% 
  select(paper_id, group_id, male:recruitment)
```

Let's check what is the most common diagnosis among the participants of the studies in the papers we have included in our overview study.

```{r}
ggplot(participants_diagnosis) +
  geom_bar(aes(diagnosis)) +
  scale_x_discrete(drop = FALSE)
```

And here are the values:

```{r, echo = FALSE, results = "asis"}
kable(
  participants_diagnosis %>% 
    group_by(diagnosis) %>% 
    count(),
  caption = "Most Common Diagnoses for Study Participants",
  col.names = c("Diagnosis", "Frequency")
)
```

We are also interested in have a look at the number of the participants' groups (identified as paper_id/group_id) that include autistic participants, comared to the groups that only have non-autistic participants.

```{r}
ggplot(participants_diagnosis_type) +
  geom_bar(aes(factor(diagnosis_type, 
                      levels = names(sort(table(diagnosis_type), 
                                          decreasing = TRUE)))))
```

```{r, echo = FALSE, results = "asis"}
kable(
  participants_diagnosis_type %>% 
    group_by(diagnosis_type) %>% 
    count() %>% 
    arrange(-n),
  caption = "Diagnosis Types",
  col.names = c("Diagnosis Type", "Frequency")
)
```


Note that some of the groups have both autistic and non-autistic participants. Therefore, the counts in the graph above don't add up to the number of groups we have, since we count those separately.



# Platform

Similarly to what we've been doing so far, we are interested in the frequency in which different platforms are used.

```{r}
platform_temp <- platform %>% 
  gather(platform_type, status, -paper_id) %>% 
  mutate(
    platform_type = factor(platform_type, levels = names(table(platform_type)))
  ) %>% 
  filter(status == 1) %>% 
  select(-status) %>% 
  mutate(
    platform_type = factor(
      platform_type,
      levels = names(sort(table(platform_type), decreasing = TRUE))
    )
  ) %>% 
  arrange(paper_id)

ggplot(platform_temp) +
  geom_bar(aes(platform_type)) +
  scale_x_discrete(drop = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Here are the actual values:

```{r, echo = FALSE, results = "asis"}
kable(
  platform_temp %>% 
    group_by(platform_type) %>% 
    count(),
  caption = "Platform Usage Frequency",
  col.names = c("Platform", "Frequency")
)
```



# Technique

Moving on to our most important table that describes the techniques used in the studies included in our overview. We will approach this table by answering some more specific questions.

## What are the roles of the *caregivers*, when a particular technique does not involve researchers?

**Note:** A specific technique is identified by paper/study/technique_id.

**Caregivers:** 

* teachers
* therapists
* caregivers
* parents 
* aut_exp
* virtual

```{r}
no_researcher_roles <- technique %>% 
  filter(res1 == 0 & res2 == 0) %>% 
  select(
    paper_id, study_id, technique_id, contains("teacher_role"), 
    contains("therapist_role"), contains("caregiver_role"), 
    contains("parent_role"), contains("aut_exp_role"), contains("virtual_role")
  ) %>% 
  gather(actor, role, -c(paper_id, study_id, technique_id)) %>% 
  filter(!is.na(role)) %>% 
  mutate(
    actor = str_sub(actor, 1, -7),
    actor = factor(actor, levels = names(sort(table(actor), decreasing = TRUE))),
    role = factor(role, levels = names(sort(table(role), decreasing = TRUE)))
  ) %>% 
  arrange(paper_id, study_id, technique_id)

ggplot(no_researcher_roles) +
  geom_bar(aes(role)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(no_researcher_roles) +
  geom_bar(aes(role)) +
  facet_wrap(~ actor, nrow = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

```{r}
kable(
  no_researcher_roles %>% 
    group_by(role) %>% 
    count(), 
  caption = "Roles of actors in studies that don't involve researchers",
  col.names = c("Role", "Frequency")
)
```


## What is the relationship among technique type, technique phase and ASD participants?

First, we need to find the paper/groups with ASD participants.

```{r}
groups_asd <- participants_temp %>% 
  filter(diagnosis_type == "ASD" | diagnosis_type == "mixed") %>% 
  select(paper_id, group_id, diagnosis, diagnosis_type)

technique_groups <- technique %>%
  select(paper_id, study_id, technique_id, technique_type, technique_phase, 
         group1, group2, group3, group4, group5, group6, group7) %>%
  gather(group_id, status, -paper_id, -study_id, -technique_id,
         -technique_type, -technique_phase) %>%
  filter(status == 1) %>%
  mutate(group_id = parse_number(group_id)) %>%
  select(-status) %>%
  arrange(paper_id, study_id, technique_id, group_id)

technique_actors <- technique %>%
  select(paper_id, study_id, technique_id, technique_type, res1, res2, teacher,
         caregiver, parent, therapist, aut_exp, designer, HCI_exp, virtual, 
         other) %>%
  gather(actor_type, status, -paper_id, -study_id, -technique_id,
         -technique_type) %>%
  filter(status > 0 | is.na(status)) %>%
  select(-status) %>%
  arrange(paper_id, study_id, technique_id)

technique_asd <- technique_groups %>% 
  semi_join(groups_asd, by = c("paper_id", "group_id"))
```

Here are the most common techniques used at each phase:

```{r}
ggplot(technique_asd) +
  geom_bar(aes(factor(technique_type, 
                      levels = names(sort(table(technique_type), 
                                          decreasing = TRUE))))) +
  facet_wrap(~ technique_phase) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

And here we see in which phase is each technique used the most:

```{r}
ggplot(technique_asd) +
  geom_bar(aes(technique_phase)) +
  facet_wrap(~ technique_type) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## What are the techniques used with participants with ASD diagnosis type?

```{r}
ggplot(technique_asd) +
  geom_bar(aes(factor(technique_type, 
                      levels = names(sort(table(technique_type), 
                                          decreasing = TRUE))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

And the values:

```{r}
kable(
  technique_asd %>% 
    group_by(technique_type) %>% 
    count() %>% 
    arrange(-n)
)
```




## Are autistic people familiarized with the environment in which the study is conducted, when the study environment is unfamiliar to them?

**Unfamiliar setting:** By *unfamiliar setting* we refer to one of the following:

* unfamiliar setting
* research lab

We want to create an additional variable for the type of place where a study is conducted.

```{r}
technique_temp <- technique %>% 
    mutate(
      place_type = ifelse(
        place %in% c("autism school", "autism center", "home", "familiar setting"),
        "familiar setting",
        ifelse(
          place %in% c("unfamiliar setting", "research lab"),
          "unfamiliar setting",
          ifelse(
            place %in% c("mixture", "other"),
            "mixture",
            NA
          )
        )
      ),
      place_type = fct_explicit_na(
        factor(place_type, levels = names(sort(table(place_type), 
                                               decreasing = TRUE))),
        na_level = "not specified"
      )
    )

familiarization <- technique_temp %>%
  filter(place_type == "unfamiliar setting") %>% 
  select(paper_id, study_id, technique_id, familiarization_person, 
         familiarization_environment) %>% 
  mutate(
    familiarization = ifelse(
      familiarization_person == 1 | familiarization_environment == 1,
      1,
      0
    )
  ) %>% 
  select(-familiarization_person, -familiarization_environment)
```


```{r}
kable(
  familiarization, 
  caption = "Familiarization of autistics with unfamiliar study settings",
  col.names = c("Paper ID", "Study ID", "Technique ID", "Familiarization")
)
```



As we can see from the table above, out of the `r nrow(familiarization)` substudies (paper/study/technique) conducted in unfamiliar settings, only `r sum(familiarization$familiarization)`, i.e. `r round(sum(familiarization$familiarization) / nrow(familiarization) * 100, digits = 2)`% of the substudies, have the autistic people been familiarized with the environment of the study in any way.

## Which technique types are used as one-shot and which ones as longitudinal?

```{r}
ggplot(technique) +
  geom_bar(aes(factor(
    technique_type, 
    levels = names(sort(table(technique_type), decreasing = TRUE))
  ))) +
  facet_wrap(~ time) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
kable(
  technique %>% 
  group_by(time) %>% 
  count()
)
```

```{r}
kable(
  technique %>% 
    group_by(technique_type, time) %>% 
    count()
)
```

## Which technique types and in which phases are used without participants?

```{r}
technique_no_participants <- technique %>% 
  filter(group1 == 0 & group2 == 0 & group3 == 0 & group4 == 0 & group5 == 0 &
           group6 == 0 & group7 == 0) %>% 
  select(-contains("group"))

ggplot(technique_no_participants) + 
  geom_bar(aes(factor(technique_type, 
                      levels = names(sort(table(technique_type),
                                          decreasing = TRUE))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

And the actual numbers of the techniques used are:

```{r}
kable(
  technique_no_participants %>% 
    group_by(technique_type) %>% 
    count() %>% 
    arrange(-n)
)
```

The total number of techniques that have no participants is `r nrow(technique_no_participants)`.

Let's now see what phases these substudies happen in.

```{r}
ggplot(technique_no_participants) + 
  geom_bar(aes(factor(technique_phase, 
                      levels = names(table(technique_phase))))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Here are the numbers of phases:

```{r}
kable(
  technique_no_participants %>% 
    group_by(technique_phase) %>% 
    count()
)
```

```{r}
ggplot(technique_no_participants) +
  geom_bar(aes(factor(technique_type, 
                      levels = names(sort(table(technique_type),
                                          decreasing = TRUE))))) +
  facet_wrap(~ technique_phase) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```

Here are the first two techniques for each phase:

```{r}
kable(
  technique_no_participants %>% 
    group_by(technique_phase, technique_type) %>% 
    count() %>% 
    ungroup() %>% 
    group_by(technique_phase) %>% 
    arrange(-n) %>% 
    slice(1:2)
)
```

## Which techniques are used for each diagnosis type, i.e. for each type of group?

```{r}
# Find the paper/study/technique combos for each paper/group combo
tech_group_temp <- technique_groups %>% 
  right_join(participants_diagnosis_type, by = c("paper_id", "group_id"))

ggplot(tech_group_temp) +
  geom_bar(aes(factor(technique_type, 
                      levels = names(sort(table(technique_type),
                                          decreasing = TRUE))))) +
  facet_wrap(~ diagnosis_type) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
kable(
  tech_group_temp %>% 
    group_by(diagnosis_type, technique_type) %>% 
    count() %>% 
    arrange(diagnosis_type, -n)
)
```


## Which techniques are used with the different roles that ASD participants are recuired to have?

```{r}
tech_group_asd <- tech_group_temp %>% 
  filter(diagnosis_type == "ASD" | diagnosis_type == "mixed")

tech_role_asd <- technique %>% 
  semi_join(tech_group_asd, by = c("paper_id", "study_id", "technique_id")) %>% 
  select(paper_id, study_id, technique_id, technique_type, 
         one_of(sprintf("group%d_role", 1:7))) %>% 
  gather(group_id, role, group1_role:group7_role) %>% 
  mutate(
    group_id = parse_number(group_id),
    role = factor(role, levels = names(table(role)))
  ) %>% 
  arrange(paper_id, study_id, technique_id, group_id) %>% 
  filter(!is.na(role)) %>% 
  mutate(role = factor(role, 
                       levels = names(sort(table(role), decreasing = TRUE))))
```

```{r}
ggplot(tech_role_asd) +
  geom_bar(aes(factor(technique_type, 
                      levels = names(sort(table(technique_type),
                                          decreasing = TRUE))))) +
  facet_wrap(~ role) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

And here are the actual values:

```{r}
kable(
  tech_role_asd %>% 
    group_by(role, technique_type) %>% 
    count() %>% 
    arrange(role, -n)
)
```


## How many techniques involve each diagnosis type of groups?

```{r}
ggplot(tech_group_temp) +
  geom_bar(aes(factor(diagnosis_type, 
                      levels = names(sort(table(diagnosis_type), 
                                          decreasing = TRUE)))))
```

```{r}
ggplot(tech_group_temp) +
  geom_bar(aes(factor(diagnosis_type, 
                      levels = names(sort(table(diagnosis_type), 
                                          decreasing = TRUE))),
               ..prop..,
              group = 1)) +
  scale_y_continuous(labels = percent)
```

```{r}
kable(
  tech_group_temp %>% 
    group_by(paper_id, study_id, technique_id) %>% 
    distinct(.keep_all = TRUE) %>% 
    ungroup() %>% 
    group_by(diagnosis_type) %>% 
    summarize(n = n()) %>% 
    mutate(
      percentage_participants = percent(n / sum(n)),
      percentage_total = percent(n / nrow(technique))
    ) %>% 
    arrange(-n)
)
```


## How many techniques involve actors?

```{r}
num_tech_actors <- technique_actors %>% 
  group_by(paper_id, study_id, technique_id) %>% 
  distinct() %>% 
  nrow()

num_tech_actors
```

And the percentage of the total number of techniques is `r percent(num_tech_actors / nrow(technique))`.

## How many techniques involve both actors and ASD participants?



## In which age categories are the ASD participants?

```{r}
participants_age_asd <- participants_age %>% 
    semi_join(groups_asd, by = c("paper_id", "group_id")) %>% 
    select(paper_id, group_id, male, female, age)
```

```{r}
ggplot(participants_age_asd) +
  geom_bar(aes(age))
```

And as percentages:

```{r}
ggplot(participants_age_asd) +
  geom_bar(aes(age, ..prop.., group = 1)) +
  scale_y_continuous(labels = percent)
```

Here are the actual values:

```{r}
kable(
  participants_age_asd %>% 
    group_by(age) %>% 
    summarize(n = n()) %>% 
    mutate(percentage = percent(n / sum(n)))
)
```
