---
title: "Quantitative Analysis"
output: html_notebook
---

```{r include = FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r, echo = FALSE}
# Loading necessary packages
library(tidyverse)
library(stringr)
library(forcats)
library(knitr)
# library(DT)

# Setting global options
options(digits = 4)
```

**Note:** In case you're not interested in the code written for the analysis, feel free to use the "Code" drop-down menu in the top-right corner and select "Hide All Code". Furthermore, the code used to produce the tables is not displayed by default (set by us).

Let's start by getting some first understanding of our data. We will look at each of our tables, one by one, and get some very basic statistics from them.

# Data Collection

Let's start by having a look at who is usually the data collector.

```{r}
data_collector_count <- data_collection %>% 
  select(data_collector) %>% 
  group_by(data_collector) %>% 
  count() %>% 
  arrange(-n)
```

```{r, echo = FALSE, results = "asis"}
kable(
  data_collector_count,
  caption = "Data Collectors",
  col.names = c("Data Collector", "Frequency")
)
```

Let's try visualizing this.

```{r}
data_collection %>% 
  group_by(data_collector) %>% 
  ggplot() +
  geom_bar(aes(x = data_collector))
```


Now, coming to the different ways of collecting the data, let's have a look at the number of times each collection menthod is used.

Let's have a look at the type of methods used first.

```{r}
collection_methods <- data_collection %>% 
  select(-c(paper_id, study_id, technique_id, data_collector)) %>% 
  colSums()

collection_methods <- tibble(method = names(collection_methods), 
                             frequency = collection_methods)

collection_methods_cat <- collection_methods %>% 
  filter(method %in% c("qualitative", "quantitative", "mixed"))
```

```{r, echo = FALSE, results = "asis"}
kable(
  collection_methods_cat, 
  caption = "Collection Methods Types Usage",
  col.names = c("Method Type", "Frequency")
)
```

Now, let's see which methoods are actually used, sorted from the most frequently used to the least frequently used.

```{r}
collection_methods_ind <- collection_methods %>%
  filter(!method %in% c("qualitative", "quantitative", "mixed")) %>% 
  arrange(-frequency)
```

```{r, echo = FALSE, results = "asis"}
kable(
  collection_methods_ind, 
  caption = "Collection Methods Most Frequently used",
  col.names = c("Method", "Frequency")
)
```

Now let's take a different approach. 

```{r}
data_collection_meth <- data_collection %>% 
  mutate(
    qualitative = ifelse(mixed == 1, 0, qualitative),
    quantitative = ifelse(mixed == 1, 0, quantitative)
  ) %>% 
  gather(method, status, -c(paper_id, study_id, technique_id, data_collector,
                            qualitative, quantitative, mixed)) %>% 
  filter(status == 1) %>% 
  select(-status) %>% 
  gather(method_type, status, -c(paper_id, study_id, technique_id, 
                                 data_collector, method)) %>% 
  filter(status == 1) %>% 
  select(paper_id, study_id, technique_id, data_collector, method_type, method,
         -status) 

ggplot(data_collection_meth) + 
  geom_bar(mapping = aes(x = method)) + 
  scale_x_discrete(limits = , drop = FALSE) +
  theme(axis.text.x = element_text(angle = 90))

# change method and method type to factors in data_collection_meth

```

